\textbf{Designing a Security Management Layer for CDN Assets}

### 2016-02-19 tex/paper.tex
Added some run-time speculations

>>>>

\subsubsection{Run-time of Operations}

\par \textbf{GET single entity} \\
When the back-end is handed a GET request it looks at what type it is and returns the document with
the correct id from the corresponding collection. As the collections are hash indexed on id this
operation can be made in constant time, O(1) and thus $\theta(1)$. \\

\par \textbf{GET project tree} \\
When requesting a project the full project tree with all entities except files has to be built as
the entities not are stored as a tree in MongoDB. The tree is built layer by layer by fetching
content with the same parent id, starting from the root of the project. Parent id's are also indexed
by a hash index which makes it possible to get all nodes with the same parent id in constant time.
This has to be done for every level with a different parent in the tree which makes the upper bound
O(n) if all of the subtrees only have one node each. The tight bound can not be calculated as the
trees balance is not determined by an algorithm but rather by a user, but from observation one 
could argue that the trees usually have several nodes for each parent node in the tree, which then
would give a logarithmic tight bound, $\theta(log(n))$.\\

\par \textbf{POST entity} \\
Creating a new entity in the system is a constant time operation for containers and content as they
only have to be inserted as new documents in MongoDB, which is a O(1)
operation~\cite{MONGOPERFOMANCE}. Even though the insertion itself has constant run-time the index 
needs to be updated or some times even rebuilt, which can slow the time before the document is
accessible in constant time. When inserting files they need to be chunked in to pieces and inserted
into GridFS, this results in n/s insertions where n is the size of the file and s is the chunk size. 
The insertion of files can then be regarded as O(n) if the size of the file is regarded, but if n is
regarded as the number of files in the system the upper bound is constant as the insertion for files
is made in the same way as for other documents.
